Backscatter Modulation Design for Symbiotic Radio Networks

### 2021-12-22 main.tex
:pencil: Remove marginal MAC

\usepackage{adjustbox}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{array}
\usepackage{circuitikz}
\usepackage{cite}
\usepackage{colortbl}
\usepackage{environ}
\usepackage{grffile}
\usepackage{hyperref}
\usepackage{import}
\usepackage{mathtools}
\usepackage{microtype}
\usepackage{multirow}
\usepackage{pgffor}
\usepackage{pgfplots}
\usepackage{physics}
\usepackage{siunitx}
\usepackage{stfloats}
\usepackage{tikz}
\usepackage{url}
\usepackage{xcolor}
\usepackage[acronym]{glossaries-extra}
\usepackage[T1]{fontenc}
\usepackage[caption=false,font=footnotesize,subrefformat=parens,labelformat=parens]{subfig}
\usepackage[short]{optidef}
% \usepackage[subtle]{savetrees}

@@

			Once the decision region is determined, we can formulate an equivalent point-to-point \gls{dmc} from tag input combination alphabet $\mathcal{M^K}$ to output energy level alphabet $\mathcal{M^K}$. The probability of receiving energy level $j$ under tag input combination $i$ is\footnote{For simplicity, we assume there exists at least one feasible precoder that produces distinct received energy levels for all tag input combinations. [TODO] Merge with precoder design.}
			\begin{equation}
				P(\bar{z}_j \mid \bar{c}_i) = P(z \in \mathcal{R}_j \mid \mathcal{H}_i) = \int_{\mathcal{R}_j} f(z \mid \mathcal{H}_i) \dd z.
				\label{eq:point_to_point_channel}
			\end{equation}

			On top of this, we can compute the marginal probability of each tag and obtain $K$ transition matrices from $\mathcal{M}$ to $\mathcal{M^K}$ that compose a discrete memoryless \gls{mac}. The probability of observing energy level $j$ when tag $k$ at state $m_k$ is
			\begin{equation}
				P(\bar{z}_j \mid \bar{c}_{m_k}) = \frac{\sum_{m_{\mathcal{K} \setminus \{k\}}} P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{\sum_{m_{\mathcal{K}}} P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}.
				\label{eq:mac}
			\end{equation}

			In summary, with the \gls{csi} knowledge and for any given precoder and detection threshold set, we can obtain the expected power of the received signal per block by \eqref{eq:receive_variance}, the conditional probability density function of the accumulated energy by \eqref{eq:energy_distribution}, the decision region by \eqref{eq:decision_region}, the equivalent point-to-point channel by \eqref{eq:point_to_point_channel}, and the discrete memoryless \gls{mac} by \eqref{eq:mac}.
		\end{subsection}

@@

			For any fixed decision boundary $\boldsymbol{t}$ and transmit precoder $\boldsymbol{w}$, the equivalent discrete memoryless \gls{mac} can be determined by \eqref{eq:mac} and problem~\eqref{op:rate_region} boils down to

@@

		% \begin{subsection}{Decision region}
		% 	As indicated by \cite{Qian2019b}, the optimal \gls{ml} decision regions are very close to the optimal decision regions to problem \eqref{op:rate_region}. We can either use \eqref{eq:decision_region} as suboptimal, or take derivative of \eqref{eq:backscatter_sum_rate} w.r.t. $T_{i-1,i}$ and $T_{i,i+1}$ (however, closed-form solutions are unavailable and two-dimensional search is needed).
		% \end{subsection}

		% \begin{subsection}{Precoder}
		% 	Interestingly, we can design precoder to adjust the expectation of the received power \eqref{eq:receive_variance} at each tag input combination, which can avoid the detection blind spots in \cite{Qian2019} and further boost the weighted sum-rate. However, the problem is highly non-convex -- the information function associated with input combination state $i$ is
		% 	\begin{align}
		% 		I(\bar{c}_i;z)
		% 		& = \sum_{j \in \mathcal{M^K}} \int_{T_{j-1,j}}^{T_{j,j+1}} \frac{z^{N-1} \exp \left(-\frac{z}{\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2}\right)}{\left(\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2\right)^N (N-1)!} \dd z\nonumber\\
		% 		& \quad \times \log \frac{\int_{T_{j-1,j}}^{T_{j,j+1}} \frac{z^{N-1} \exp \left(-\frac{z}{\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2}\right)}{\left(\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2\right)^N (N-1)!} \dd z}{\sum_{i' \in \mathcal{M^K}} \int_{T_{j-1,j}}^{T_{j,j+1}} \frac{z^{N-1} \exp \left(-\frac{z}{\mathrm{tr}(H_{\mathrm{E},i'} W) + \sigma_w^2}\right)}{\left(\mathrm{tr}(H_{\mathrm{E},i'} W) + \sigma_w^2\right)^N (N-1)!} \dd z},
		% 		\label{eq:foo}
		% 	\end{align}
		% 	and the mutual information can be expressed as a function of $W$ by combining \eqref{eq:backscatter_sum_rate} and \eqref{eq:foo}.

		% 	So far I have no idea how to solve this issue, and found no reference regarding precoder design for \gls{ambc}/\gls{sr} with discrete channels (although some naive combiner designs are available for \gls{bibo}). Personally, I believe the precoder design is the key to (i) boost the rate region and avoid blind spots in conventional \gls{ambc}; (ii) build our proposal over existing infrastructures. Ideally, assuming the number of transmit antennas $Q$ is larger than the number of tags $K$, the optimal energy levels should be almost uniformly spaced (as $z$ follows Erlang distribution) to concentrate the channel transitional probability on diagonal as possible.
		% \end{subsection}
	\end{section}
	\bibliographystyle{IEEEtran}
	\bibliography{IEEEabrv,library.bib}
\end{document}

>>>>

\usepackage{adjustbox}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{array}
\usepackage{circuitikz}
\usepackage{cite}
\usepackage{colortbl}
\usepackage{environ}
\usepackage{grffile}
\usepackage{hyperref}
\usepackage{import}
\usepackage{mathtools}
\usepackage{microtype}
\usepackage{multirow}
\usepackage{pgffor}
\usepackage{pgfplots}
\usepackage{physics}
\usepackage{siunitx}
\usepackage{stfloats}
\usepackage{tikz}
\usepackage{url}
\usepackage{xcolor}
\usepackage[acronym]{glossaries-extra}
\usepackage[T1]{fontenc}
\usepackage[caption=false,font=footnotesize,subrefformat=parens,labelformat=parens]{subfig}
\usepackage[short]{optidef}
% \usepackage[subtle]{savetrees}
\usepackage{stmaryrd}

@@

			Once the decision region is determined, the discrete memoryless \gls{mac} can be recast as an equivalent point-to-point \gls{dmc} from tag input combination alphabet $\mathcal{M^K}$ to output energy level alphabet $\mathcal{M^K}$. The the probability of receiving energy level $j$ under tag input combination $i$ is\footnote{For simplicity, we assume there exists at least one feasible precoder that produces distinct received energy levels for all tag input combinations. [TODO] Merge with precoder design.}
			\begin{equation}
				P(\bar{z}_j \mid \bar{c}_i) = P(z \in \mathcal{R}_j \mid \mathcal{H}_i) = \int_{\mathcal{R}_j} f(z \mid \mathcal{H}_i) \dd z,
				\label{eq:point_to_point_channel}
			\end{equation}
			which corresponds to $P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})$ by reverse mapping $m_k \mapsfrom i$. In summary, with the \gls{csi} knowledge and for any given precoder and detection threshold set, we can obtain the expected power of the received signal per block by \eqref{eq:receive_variance}, the conditional probability density function of the accumulated energy by \eqref{eq:energy_distribution}, the corresponding decision region by \eqref{eq:decision_region}, and the equivalent point-to-point channel by \eqref{eq:point_to_point_channel}.
		\end{subsection}

@@

			For any fixed decision boundary $\boldsymbol{t}$ and transmit precoder $\boldsymbol{w}$, the equivalent discrete memoryless \gls{mac} can be determined by \eqref{eq:point_to_point_channel} and problem~\eqref{op:rate_region} boils down to

@@

		\begin{subsection}{Decision region}
			As indicated by \cite{Qian2019b}, the optimal \gls{ml} decision regions are very close to the optimal decision regions to problem \eqref{op:rate_region}. We can either use \eqref{eq:decision_region} as suboptimal, or take derivative of \eqref{eq:backscatter_sum_rate} w.r.t. $T_{i-1,i}$ and $T_{i,i+1}$ (however, closed-form solutions are unavailable and two-dimensional search is needed).
		\end{subsection}

		\begin{subsection}{Precoder}
			Interestingly, we can design precoder to adjust the expectation of the received power \eqref{eq:receive_variance} at each tag input combination, which can avoid the detection blind spots in \cite{Qian2019} and further boost the weighted sum-rate. However, the problem is highly non-convex -- the information function associated with input combination state $i$ is
			\begin{align}
				I(\bar{c}_i;z)
				& = \sum_{j \in \mathcal{M^K}} \int_{T_{j-1,j}}^{T_{j,j+1}} \frac{z^{N-1} \exp \left(-\frac{z}{\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2}\right)}{\left(\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2\right)^N (N-1)!} \dd z\nonumber\\
				& \quad \times \log \frac{\int_{T_{j-1,j}}^{T_{j,j+1}} \frac{z^{N-1} \exp \left(-\frac{z}{\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2}\right)}{\left(\mathrm{tr}(H_{\mathrm{E},i} W) + \sigma_w^2\right)^N (N-1)!} \dd z}{\sum_{i' \in \mathcal{M^K}} \int_{T_{j-1,j}}^{T_{j,j+1}} \frac{z^{N-1} \exp \left(-\frac{z}{\mathrm{tr}(H_{\mathrm{E},i'} W) + \sigma_w^2}\right)}{\left(\mathrm{tr}(H_{\mathrm{E},i'} W) + \sigma_w^2\right)^N (N-1)!} \dd z},
				\label{eq:foo}
			\end{align}
			and the mutual information can be expressed as a function of $W$ by combining \eqref{eq:backscatter_sum_rate} and \eqref{eq:foo}.

			So far I have no idea how to solve this issue, and found no reference regarding precoder design for \gls{ambc}/\gls{sr} with discrete channels (although some naive combiner designs are available for \gls{bibo}). Personally, I believe the precoder design is the key to (i) boost the rate region and avoid blind spots in conventional \gls{ambc}; (ii) build our proposal over existing infrastructures. Ideally, assuming the number of transmit antennas $Q$ is larger than the number of tags $K$, the optimal energy levels should be almost uniformly spaced (as $z$ follows Erlang distribution) to concentrate the channel transitional probability on diagonal as possible.
		\end{subsection}
	\end{section}
	\bibliographystyle{IEEEtran}
	\bibliography{IEEEabrv,library.bib}
\end{document}
